---
title: "Interactive Visualization: Adjusted Gross Revenue, Year, MPAA Rating of Top Movies (Domestic)"
output: html_document
date: "2025-03-24"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r message=FALSE}

library(readxl)

movies_data  <- read_excel("~/Desktop/Semester 2/Data Visualization/Assignments/Final Project/Top-Movie-Per-Year-Individual.xlsx")
```

## Notes

The interactive plots show "Adjusted Gross" twice when hovering over a data point. I could not figure out how to correct that.

### Basic/Static ggplot
```{r message=FALSE}
# Load packages
library(ggplot2)
library(dplyr)
library(gapminder)
library(dplyr)
library(plotly)


movies_data$unfactored_mpaa <- movies_data$`MPAA rating`

movies_data$`MPAA rating` <- factor(movies_data$`MPAA rating`, levels = c("G", "PG", "PG-13", "R")) 

movie_ggplot <-
  ggplot(movies_data, 
         aes(x = Year, y = `Adjusted Gross`, 
             size = `Adjusted Gross`, 
             fill = `MPAA rating`,
             text = paste("Movie:", `Number 1 Release`))) +
  geom_point(alpha = 0.5, shape = 21, stroke = 0.5, color = 'black', 
             position = position_jitter(height = 0)) +
  scale_y_continuous(labels = scales::dollar_format()) +
  scale_size_continuous(range = c(1, 10), 
                        labels = function(x) paste0(round(x / 1e9, 1), "B")) +
  labs(title = "Adjusted Gross Revenue, Year, MPAA Rating of Top Movies (Domestic)",x = "Year", y = "Adjusted Gross (USD)") + 
  theme_minimal() +
  guides(fill = guide_legend(override.aes = list(size = 5)))

movie_ggplot

```


# Interactive Bubble Plot
### Full Plot Title: Comparing Adjusted Gross Revenue of Top Movies (Domestic): Year and MPAA Rating

(plotly cut off the rest of the title and didn't know how to fix)

```{r message=FALSE}
plotly_interactive <- ggplotly(movie_ggplot)

#plotly_interactive <- plotly::style(plotly_interactive, marker = list(line = list(width = 0.5)))

plotly_interactive

```



# Alternative Interactive Scatter Plot

```{r echo = FALSE}
movie_ggplot2 <-
  ggplot(movies_data, 
         aes(x = Year, y = `Adjusted Gross`, 
             size = `Adjusted Gross`, 
             fill = `MPAA rating`,
             text = paste("Movie:", `Number 1 Release`))) +
  geom_point(alpha = 0.5, 
             position = position_jitter(height = 0)) +
  scale_y_continuous(labels = scales::dollar_format()) +
  scale_size_continuous(range = c(1, 10), 
                        labels = function(x) paste0(round(x / 1e9, 1), "B")) +
  labs(title = "Adjusted Gross Revenue, Year, MPAA Rating of Top Movies (Domestic)",x = "Year", y = "Adjusted Gross (USD)") + 
  theme_minimal() +
  guides(fill = guide_legend(override.aes = list(size = 5)))
```


```{r}
plotly_interactive2 <- ggplotly(movie_ggplot2, sizes = c(10, 30))

plotly_interactive2 <- plotly::style(plotly_interactive2, marker = list(line = list(width = 0.5)))

plotly_interactive2

```


